### 2023-06-13 paper/main.tex
..

\section{Introduction}

@@

>>>>

\section{Introduction}
The aim of sound field synthesis is to reproduce a virtual target sound field over an extended listening area using a densely spaced loudspeaker arrangement, known as the secondary source distribution (SSD).
By feeding the loudspeakers with specific driving functions, the superposition of sound fields from each SSD element should ideally match the target sound field in the intended receiving area.
One prominent sound field synthesis method is Wave Field Synthesis (WFS) \cite{Berkhout1993:Acoustic_control_by_WFS, Start1997:phd}.%, which obtains the necessary driving functions from a suitable boundary integral representation of the target sound field.

@@

\section{Conclusion}
